Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-02-01 cogsci2016/paper.tex
figures
comments Arthur

	In this paper we focus on the study of this progression between overlapping phases of behaviours with objects in a robotic model and in particular on the use of concurrent methods to solve a problem.	
	We hypothesize that several mechanisms play a role in the structure of this behavioural progression and in particular 
	1) the intrinsic motivation to explore as a self-regulation of the learning growth of complexity, and 
	2) the structure of the representation used to encode sensorimotor experience.	
	Active learning is a paradigm where the learning agent chooses which actions to perform in its environment.
	To make this choice the agent can optimize some extrinsic rewards given by the environment, as in standard Reinfocement Learning tasks.
	These extrinsic rewards are not suited for an open-ended autonomous exploration of the environment that could reflect children learning by free play.
	Based on infant's developmental psychology, different types of intrinsic motivations have been studied \cite{santucci2013}.
	One way to define an intrinsic motivation is to autonomously search for situations where the learning progress is high, so as to avoid unreachable or unlearnable situations.
	Computational models have shown that developmental trajectories could emerge from the curiosity-driven learning of sensorimotor mappings, in very different settings.
	In the Playground Experiment \cite{oudeyer_what_2007}, a quadruped robot learned how to use its motor primitives to interact with the items of an infant play mat and a robot peer.
	Also, in a study of the self-organization of vocalizations \cite{moulin-frier_self-organization_2014}, an agent had to learn how to
	use a vocal synthesizer by self-exploration or with the help of humans' demonstrations of phonetic items. 
	This model reproduces accurately major phases of infant vocal development until $6$ months.
	In both studies, developmental trajectories of increasing complexity are emerging from learning, with both regularities in developmental steps and diversity.
	The diversity comes from different mechanisms: stochasticity in the algorithms, variability in the environment, and the multiples attractors of the dynamic learning system.
	In existing models, the agent learns only one mapping that relates a motor space to a single task space. 
	However, in the perspective of an open-ended development of reusable skills, and specifically in the development of tool use, multiple interdependent and hierarchically organized task spaces should be available to the agent
	as for instance using a tool to act upon an object could make use of previously explored parameterized interaction with the tool.

@@

		We simulate a 2D robotic arm that can grasp tools that can be used to move an object into different boxes in the environment. 		
		In each trial, the agent executes a motor trajectory, we evaluate its consequences on the sensory dimensions and we give him
		this sensory feedback. Finally the arm, tools and objects are resetted to their intial state.
		The next sections precisely describe the items of the environment and their interactions.	
		See Fig.\ref{env} for an exemple state of the environment.

@@

		\subsubsection{Robotic arm}

@@

		\subsubsection{Motor control}

@@

		\subsubsection{Objects and tools}

			Two sticks can be grasped by the handle side in order to catch an out-of-reached object.
			A small stick of length $0.3$ is located at position $(0.75, 0.25)$ with initial angle $\frac{\pi}{4}$ from the horizontal line.
			A long stick of length $0.6$ is located at position $(-0.75, 0.25)$ with initial angle $\frac{3\pi}{4}$ as in Fig. \ref{env}.	
			A yellow sphere can be caught by the magnetic side of one of the two sticks, moved and possibly placed into one of ten fixed squared boxes. 
			The initial position of the sphere is $(0, 1.2)$ and is thus unreachable directly with the gripper.		
			If the gripper is closed near the handle of one stick (closer than $0.2$), it is considered grasped and will follow the gripper's position and the angle of the arm's last segment until the gripper opens.			
			Similarly, if the other end of a stick reaches the sphere (within $0.1$), the sphere will follow the end of the stick.
			The ten boxes (identified from $1$ to $10$) are static and have size $0.2$.
			Boxes $1$ to $5$ can only be reached with the long stick, and the other five boxes can be reached with both sticks.
			At the end of the movement, the object is considered to be in one of the box if its center is in the box.

@@

		\subsubsection{Sensory feedback}

@@

	\subsection{Learning architectures}

@@

		\subsubsection{Flat architectures}

@@

			The agent also needs an interest model that chooses goals in the sensory space.
			The control condition is a random motor babbling condition (F-RmB) that randomly chooses new motor parameters $m$ to try at each iteration.
			In the other conditions, the agent performs Goal Babbling, a method by which it self-generates a goal in the sensory space at each iteration and trying to reach it.
			To generate those goals, different strategies have been studied \cite{baranes_active_2013}. 
			It was shown that estimating the learning progress in different regions of the sensory space and generating the goals where the progress is high leads to a fast learning.
			However, this idea cannot be applied in a $25$D sensory space as a learning progress signal cannot be properly estimated in this volume.
			Thus we use a simpler random generation of goals in the sensory space as an interest model in the flat random goal babbling condition (F-RGB), 
			which was nevertheless proven to be highly efficient in complex sensorimotor spaces \cite{rolf}.
			We use the Explauto autonomous exploration library \cite{moulin-frier_explauto:_2014} to easily define those sensorimotor and interest models.

@@

		\subsubsection{Hierarchical architectures}

			The $25$D sensory space can be structured to reflect the interaction of the different items of the environment.
			Indeed, the arm motor position influence the gripper, which influence one of the tools (but not both at the same time), which influence the position of the object and the filling of the boxes.
			We thus study here learning architectures that could make use of this sensorimotor structure, and we call them hierarchical.
			%\footnote{Other work have used a simple hierarchy of two sensorimotor models for object manipulation: \cite{forestier2015} and \cite{unifying}.}
			Those architecture learn $6$ models at the same time (see Fig. \ref{Architectures}: gray squares are models). 
			Each of those models functions in the same way as the random goal babbling flat architecture (F-RGB). 
			Each model has a motor space (e.g. motor space of model $2$ is $S_{Hand}$), a sensory space (respectively $S_{Stick_1}$, see arrows in Fig. \ref{Architectures}, and can choose goals randomly in this sensory space.
			At each iteration, the architecture first have to choose the model in which to choose a goal, a procedure that we call Model Babbling.
			Once a model is chosen, it finds a goal in its sensory space, and infer motor parameters (that can be in the sensory space of a lower-level model) to reach that goal.
			Then, it passes those parameters as a goal to be reached by a lower-level model, 
			which similarly infers motor parameters and passes those ones until the actual $Arm$ motor space gets parameters to try in the environment (with the same exploration noise as in Flat architectures).
			Model $4$ have also to choose which lower-level model to use in order to reach an object end position $s_o$ in $S_{Object}$, as two models ($3$ and $6$) have $S_{Object}$ as sensory space. 
			Model $4$ chooses the tool that have allowed to reached $s_o$ as close as possible in the past, e.g. if model $3$ has in its history a reached sensory
			point $s$ closer to $s_o$ than any reached point with model $6$, then model $3$ is chosen.
			Finally, when motor parameters $m$ have been tested in the environment and feedback $s$ received, the mappings of all models are updated, but if model $4$ have chosen a given tool, then the mapping of the other tool is not.

@@

			\begin{equation}
				C(s_g)=-\frac{||s_g-s||}{max_{s'}||s'-s||}
			\end{equation}
			 and the interest $I(s_g)$ associated to this goal as 
			\begin{equation}
				I(s_g) = |C(s_g) - mean_{kNN}C(s)|
			\end{equation}
			the absolute difference between $C(s_g)$ and the mean competence of the ($k=20$) nearest previous goals.
			The interest of a model is initialized at $0$ and updated to follow the interest of the goals (with rate $n=200$):
			\begin{equation}
				I_{model}=\frac{n-1}{n}~I_{model} + \frac{1}{n}~I(s_g)
			\end{equation}
			In condition H-P-AMB, the choice of model is probabilistic and proportional to their interest (but with $\epsilon=10\%$ of random choice). 
			In condition H-GR-AMB, the choice of model is greedy (model with maximum interest) but also with $\epsilon=10\%$ of random choice.
			Finally, condition H-P-AMB-ATC is the same as H-P-AMB but the choice of the tool to use (model $3$ or $6$) is with probabilities proportional to the interest of the two models, 
			instead of being based on the more competent tool for the given object goal position.
			We call HACOB this Hierarchical Active Curiosity-driven mOdel Babbling algorithmic architecture with the algorithms H-P-AMB and H-P-AMB-ATC being two variants of the architecture.

@@

	\subsubsection{Structure of the evolution of behaviours}

@@

		\begin{figure*}[ht]
			\centering
			\includegraphics[width=5.5cm]{./include/F-RGB-log53-events-100000.pdf}
			\hspace{-0.4cm}
			\includegraphics[width=5.5cm]{./include/H-RGB-GR-AMB-log13-events-100000.pdf}
			\hspace{-0.4cm}
			\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log38-events-100000.pdf}
			\caption{Behavioural phases typical exemples. Left: F-RGB. Middle: H-GR-AMB, Right: H-P-AMB. Only hierarchical active condition H-P-AMB shows overlapping phases of behaviour similar to infant development.}
			\label{res_ow}
		\end{figure*}

@@

	\subsubsection{Exploration efficiency}

		Also, for each condition we measure the total exploration of the different sensory spaces during training. 
		The exploration of the hand, sticks and object spaces is defined as the number of reached cells 
		in a $100\times100$ discretization of the (X,Y) space of the position at timestep $50$ (end of movement).
		The exploration of the boxes is the number of boxes that have been filled with the object during training.
		Fig. \ref{res_explo} shows the total exploration of the different sensory spaces for each condition.
		We provide statistical Mann-Whitney U test results of comparisons of the exploration in different pairs of conditions.
		Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
		Then, F-RGB explores all spaces less than H-RMB condition ($p<0.01$).
		H-RMB explores more $S_{Hand}$ ($p<0.001$) and less $S_{Object}$ ($p<0.05$) than H-P-AMB.
		Also, H-GR-AMB shows lower exploration all spaces than H-P-AMB ($p<0.01$).
		Condition H-P-AMB-ATC explores more $S_{Stick_2}$ ($p<0.05$) than condition H-P-AMB, and difference is not significant in other spaces.

@@

	\subsubsection{Structure of tool choice}

		Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H-P-AMB and H-P-AMB-ATC.
		In those conditions, model $4$ learns a mapping between $S_{Object}$ and $S_{Boxes}$. 
		When this model is babbling, it chooses a random goal $s_b \in S_{Boxes}$ and infers the best object position $s_o$ to reach $s_b$.
		To reach $s_o$, one of the tools ($Stick_1$ with model $3$ or $Stick_2$ with model $6$) is chosen. 
		We plot all those choices model $4$ made during exploration, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, in one figure for each of the two conditions.
		We can see two very different choice structures.
		However, goal that can be reached with both tools are more often chosen to be explored with the long stick in the interest-based choice of condition H-P-AMB-ATC than in competence-based choice of condition H-P-AMB.

		\begin{figure}[ht]
			\centering
			\includegraphics[width=4.3cm]{./include/choice-H-RGB-P-AMB.pdf}
			\hspace{-0.2cm}
			\includegraphics[width=4.3cm]{./include/choice-H-RGB-P-AMB-PGITC.pdf}
			\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: condition H-P-AMB, strong boundaries 
			between tool choice regions. Right: condition H-P-AMB-ATC, parallel exploration of both tools for the same goals.}
			\label{res_choice}
		\end{figure}

@@

	\subsubsection{Structure of the evolution of behaviours}

		Results show different structures of behaviour evolution in the different conditions.		
		Flat architectures do not use the structure of the environment and do not separate the high-dimensional sensorimotor space into learnable subspaces.
		Therefore, they do not show structure in the behavioural evolution but rather steady proportions of the three behaviours.
		By contrast, hierarchical condition H-GR-AMB shows successive behavioural steps with abrupt changes, which reflects the greedy choice of model to babble.
		When one model becomes more interesting than another, it is chosen
		for a large number of iterations until another model exceeds its interest.
		However, random model babbling shows overlapping phases structures in the evolution of the three behaviours more compatible with infants' studies ($60\%$), 
		but less than active model babbling ($70\%$ and $79\%$).
		This is because random model babbling does not adapt its choice of models to their interests along development.
		Indeed, it often explores model $1$ even if it is sufficiently explored to make progress on higher-level models, 
		and so explores less the object position space than active model babbling (H-P-AMB).
		Also, in this setup, all models are still useful to explore after the number of iterations simulated 
		here so the first behavioural phases ($hand$ and $stick$) do not lessen towards the end of the simulations in active conditions. 
		Consequently, the difference between active and random model babbling is more on the cognitive or intentional level, 
		as active model babbling monitors the current progress of each model whereas random model babbling do not, than on a quantitative level.
		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, active model babbling would
		make a key difference on a quantitative exploration point of view and on the structure of the evolution of the measured behaviours.

@@

	\subsubsection{Variability of strategies to reach goals}

@@

	Finally, in our model, H is determinant and A reinforces the emergence of structures.
	Link with children ?
	First model to

>>>>

	In this paper we focus on the study of this progression between overlapping phases of behaviours with objects in a robotic model and in particular on the use of concurrent methods to solve a problem.	
	We hypothesize that several mechanisms play a role in the structure of this behavioural progression and in particular 
	1) the intrinsic motivation to explore as a self-regulation of the learning growth of complexity, and 
	2) the structure of the representation used to encode sensorimotor experience.	
	Active learning is a paradigm where the learning agent chooses which actions to perform in its environment.
	To make this choice the agent can optimize some extrinsic rewards given by the environment, as in standard Reinfocement Learning tasks.
	These extrinsic rewards are not suited for an open-ended autonomous exploration of the environment that could reflect children learning by free play.
	Based on infant's developmental psychology, different types of intrinsic motivations have been studied \cite{santucci2013}.
	One way to define an intrinsic motivation is to autonomously search for situations where the learning progress is high, so as to avoid unreachable or unlearnable situations.
	Computational models have shown that developmental trajectories could emerge from the curiosity-driven learning of sensorimotor mappings, in very different settings.
	In the Playground Experiment \cite{oudeyer_what_2007}, a quadruped robot learned how to use its motor primitives to interact with the items of an infant play mat and a robot peer.
	Also, in a study of the self-organization of vocalizations \cite{moulin-frier_self-organization_2014}, an agent had to learn how to
	use a vocal synthesizer by self-exploration or with the help of humans' demonstrations of phonetic items. 
	This model reproduces accurately major phases of infant vocal development until $6$ months.
	In both studies, developmental trajectories of increasing complexity are emerging from learning, with both regularities in developmental steps and diversity.
	The diversity comes from different mechanisms: stochasticity in the algorithms, variability in the environment, and the multiples attractors of the dynamic learning system.
	In existing models, the agent learns only one mapping that relates a motor space to a single task space. 
	However, in the perspective of an open-ended development of reusable skills, and specifically in the development of tool use, multiple interdependent and hierarchically organized task spaces should be available to the agent.
	For instance, using a tool to act upon an object could make use of previously explored parameterized interaction with the tool.

@@

		We simulate a 2D robotic arm that can grasp tools that can be used to move an object into different boxes in the environment. 		
		In each trial, the agent executes a motor trajectory and gets the associated sensory feedback. 
		Finally the arm, tools and objects are resetted to their intial state.
		The next sections precisely describe the items of the environment and their interactions.	
		See Fig.\ref{env} for an exemple state of the environment.

@@

		\subsubsection{Robotic Arm}

@@

		\subsubsection{Motor Control}

@@

		\subsubsection{Objects and Tools}

			Two sticks can be grasped by the handle side in order to catch an out-of-reach object.
			A small stick of length $0.3$ is located at position $(0.75, 0.25)$ with initial angle $\frac{\pi}{4}$ from the horizontal line.
			A long stick of length $0.6$ is located at position $(-0.75, 0.25)$ with initial angle $\frac{3\pi}{4}$ as in Fig. \ref{env}.	
			A yellow sphere can be caught by the magnetic side of one of the two sticks, moved and possibly placed into one of ten fixed squared boxes. 
			The initial position of the sphere is $(0, 1.2)$ and is thus unreachable directly with the gripper.		
			If the gripper is closed near the handle of one stick (closer than $0.2$), it is considered grasped and follows the gripper's position and the angle of the arm's last segment until the gripper opens.			
			Similarly, if the magnetic side of a stick reaches the sphere (within $0.1$), the sphere will then follow the magnet.
			The ten boxes (identified from $1$ to $10$) are static and have size $0.2$.
			Boxes $1$ to $5$ can only be reached with the long stick, and the other five boxes can be reached with both sticks.
			At the end of the movement, the object is considered to be in one of the box if its center is in the box.

@@

		\subsubsection{Sensory Feedback}

@@

	\subsection{Learning Architectures}

@@

		\subsubsection{Flat Architectures}

@@

			The agent also needs an interest model that chooses goals in the sensory space.
			The control condition is a random motor babbling condition (F-RmB) that randomly chooses new motor parameters $m$ to try at each iteration.
			In the other conditions, the agent performs Goal Babbling, a method by which it self-generates a goal in the sensory space at each iteration and tries to reach it.
			To generate those goals, different strategies have been studied \cite{baranes_active_2013}. 
			It was shown that estimating the learning progress in different regions of the sensory space and generating the goals where the progress is high leads to a fast learning.
			However, this idea cannot be applied in a $25$D sensory space as a learning progress signal cannot be properly estimated in this volume.
			Thus we use a simpler random generation of goals in the sensory space as an interest model in the flat random goal babbling condition (F-RGB), 
			which was nevertheless proven to be highly efficient in complex sensorimotor spaces \cite{rolf}.
			We use the Explauto autonomous exploration library \cite{moulin-frier_explauto:_2014} to easily define those sensorimotor and interest models.

@@

		\subsubsection{Hierarchical Architectures}

			The $25$D sensory space can be structured to reflect the interaction of the different items of the environment.
			Indeed, the arm motor position influence the gripper, which influence one of the tools (but not both at the same time), which influence the position of the object and the filling of the boxes.
			We thus study here learning architectures that could make use of this sensorimotor structure, and we call them hierarchical.
			%\footnote{Other work have used a simple hierarchy of two sensorimotor models for object manipulation: \cite{forestier2015} and \cite{unifying}.}
			Those architecture learn $6$ models at the same time (see Fig. \ref{Architectures}: gray squares are models). 
			Each of those models functions in the same way as the random goal babbling flat architecture (F-RGB). 
			Each model has a motor space (e.g. motor space of model $2$ is $S_{Hand}$), a sensory space (respectively $S_{Stick_1}$, see arrows in Fig. \ref{Architectures}), and can choose goals randomly in this sensory space.
			At each iteration, the architecture first have to choose the model in which to choose a goal, a procedure that we call Model Babbling.
			Once a model is chosen, it finds a goal in its sensory space, and infer motor parameters (that can be in the sensory space of a lower-level model) to reach that goal.
			Then, it passes those parameters as a goal to be reached by a lower-level model, 
			which similarly infers motor parameters and passes those ones until the actual $Arm$ motor space gets parameters to try in the environment (with the same exploration noise as in Flat architectures).
			Model $4$ have also to choose which lower-level model to use in order to reach an object end position $s_o$ in $S_{Object}$, as two models ($3$ and $6$) have $S_{Object}$ as sensory space. 
			Model $4$ chooses the tool that have allowed to reached $s_o$ as close as possible in the past, e.g. if model $3$ has in its history a reached sensory
			point $s$ closer to $s_o$ than any reached point with model $6$, then model $3$ is chosen.
			Finally, when motor parameters $m$ have been tested in the environment and feedback $s$ received, the mappings of all models are updated, but if model $4$ have chosen a given tool, then the mapping of the other tool is not.

@@

			\begin{equation}
				C(s_g)=-\frac{||s_g-s||}{max_{s'}||s'-s||}
			\end{equation}
			 and the interest $I(s_g)$ associated to this goal as 
			\begin{equation}
				I(s_g) = |C(s_g) - mean_{kNN}C(s)|
			\end{equation}
			the absolute difference between $C(s_g)$ and the mean competence of the ($k=20$) nearest previous goals (k-Nearest Neighbours algorithm).
			The interest of a model is initialized at $0$ and updated to follow the interest of the goals (with rate $n=200$):
			\begin{equation}
				I_{model}=\frac{n-1}{n}~I_{model} + \frac{1}{n}~I(s_g)
			\end{equation}
			In condition H-P-AMB, the choice of model is probabilistic and proportional to their interest (but with $\epsilon=10\%$ of random choice). 
			In condition H-GR-AMB, the choice of model is greedy (model with maximum interest) but also with $\epsilon=10\%$ of random choice.
			Finally, condition H-P-AMB-ATC is the same as H-P-AMB but the choice of the tool to use (model $3$ or $6$) is with probabilities proportional to the interest of the two models, 
			instead of being based on the more competent tool for the given object goal position.
			We call HACOB this Hierarchical Active Curiosity-driven mOdel Babbling algorithmic architecture with the algorithms H-P-AMB and H-P-AMB-ATC being two variants of the architecture.

@@

	\subsubsection{Structure of the Evolution of Behaviours}

@@

		\begin{figure*}[ht]
			\centering
			\includegraphics[width=5.5cm]{./include/F-RGB-log53-events-100000.pdf}
			\includegraphics[width=5.5cm]{./include/H-RGB-GR-AMB-log13-events-100000.pdf}
			\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log38-events-100000.pdf}
			\caption{Behavioural phases typical exemples. Left: F-RGB. Middle: H-GR-AMB, Right: H-P-AMB. Only hierarchical active condition H-P-AMB shows overlapping phases of behaviour similar to infant development.}
			\label{res_ow}
		\end{figure*}

@@

	\subsubsection{Exploration Efficiency}

		Also, for each condition we measure the total exploration of the different sensory spaces during training. 
		The exploration of the hand, sticks and object spaces is defined as the number of reached cells 
		in a $100\times100$ discretization of the (X,Y) space of their position at the end of the movement.
		The exploration of the boxes is the number of boxes that have been filled with the object during training.
		Fig. \ref{res_explo} shows the total exploration of the different sensory spaces for each condition.
		We provide statistical Mann-Whitney U test results of comparisons of the exploration for some pairs of conditions.
		One star means $p<0.05$, two: $p<0.01$, three: $p<0.001$ and four: $p<0.0001$.
		%Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
		%Then, F-RGB explores all spaces less than H-RMB condition ($p<0.01$).
		%H-RMB explores more $S_{Hand}$ ($p<0.001$) and less $S_{Object}$ ($p<0.05$) than H-P-AMB.
		%Also, H-GR-AMB shows lower exploration of all spaces than H-P-AMB ($p<0.01$).
		%Condition H-P-AMB-ATC explores more $S_{Stick_2}$ ($p<0.05$) than condition H-P-AMB, and difference is not significant in other spaces.

@@

	\subsubsection{Structure of Tool Choice}

		Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H-P-AMB and H-P-AMB-ATC.
		When model $4$ is babbling, it infers the best object position $s_o$ to reach a random goal $s_b \in S_{Boxes}$.
		To reach $s_o$, one of the tools ($Stick_1$ with model $3$ or $Stick_2$ with model $6$) is chosen. 
		We plot all the choices that model $4$ made during exploration, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, 
		in one figure for each of the two conditions.
		In condition H-P-AMB, we can see strong boundaries between tool choice regions.
		By contrast, in condition H-P-AMB-ATC, both tools are chosen in all regions.

		\begin{figure}[ht]
			\centering
			\includegraphics[width=4.3cm]{./include/choice-H-RGB-P-AMB.pdf}
			\hspace{-0.2cm}
			\includegraphics[width=4.3cm]{./include/choice-H-RGB-P-AMB-PGITC.pdf}
			\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: condition H-P-AMB, strong boundaries 
			between tool choice regions. Right: condition H-P-AMB-ATC, parallel exploration of both tools in all regions.}
			\label{res_choice}
		\end{figure}

@@

	\subsubsection{Structure of the Evolution of Behaviours}

		Results show different structures of behaviour evolution in the different conditions.		
		Flat architectures do not use the structure of the environment and do not separate the high-dimensional sensorimotor space into learnable subspaces.
		Therefore, they do not show structure in the behavioural evolution but rather steady proportions of the three behaviours.
		By contrast, hierarchical condition H-GR-AMB shows successive behavioural steps with abrupt changes, which reflects the greedy choice of model to babble.
		When one model becomes more interesting than another, it is chosen
		for a large number of iterations until another model exceeds its interest.
		However, random model babbling shows overlapping phases structures in the evolution of the three behaviours more compatible with infants' studies ($60\%$), 
		but less than active model babbling ($70\%$ and $79\%$).
		This is because random model babbling does not adapt its choice of models to their interests along development.
		Indeed, it often explores model $1$ even if it is sufficiently explored to make progress on higher-level models, 
		and so explores less the object position space than active model babbling (H-P-AMB).
		Also, in this setup, all models are still useful to explore after the number of iterations simulated 
		here so the first behavioural phases ($hand$ and $stick$) do not lessen towards the end of the simulations in active conditions. 
		Consequently, the difference between active and random model babbling is more on the cognitive or intentional level, 
		as active model babbling monitors the current progress of each model whereas random model babbling do not, than on a quantitative level.
		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, active model babbling would
		make a key difference on a quantitative exploration point of view and on the structure of the evolution of the measured behaviours.\\

@@

	\subsubsection{Variability of Strategies to Reach Goals}

@@

	Finally, in our model, the hierarchical structure is a determining factor for the emergence of structured behavioural phases, and the active learning reinforces this emergence.
	Link with children ?
	First model to ?
